\section{Flutter}

Seção 1: Introduction
1. What You?ll Learn From This Course?

Hi everyone this is Farid-ul-Haq or AJ Raven.

For those of you wondering about my name let me begin by saying thank you to all of you who decided

to try this course I made as the name suggests this is a very basic course about Google flutter and

dart you can think of it as a Pre Google flutter and dart course which means that I will be going

over the information you require to get an idea about what this meant by Flutter and why app developers

using it.

The benefits it offers and whether or not it's something you might wish to know more about the same

goes for dart.

I will be going over the basics of Dart especially why it is used by flutter and more app development

has gained a lot of traction over the years and there's a lot of profit to be earned.

If you are able to create an app that catches the attention of the public of the public and flutter might be the

tool you require to create such an app. Coming to this course.

Everything has been divided into different sections.

I begin by talking about flutter and then move on to dart.

I have tried to deliver all of the information in the most basic manner possible to help even those

of you who haven't heard of flutter or dart before.

So without further ado let's begin with this course.



2. Whats is Flutter?

Let's begin with the first take what it's flirter for those of you who might not know Google flirter

as the name implies is Google's mobile app SDK which can be used for crafting high quality native interfaces

on both iOS and Android in a short amount of time.

The initial release of flirter was in May of 2017.

Also a side note SDK stands for software development.

Good.

You should know that flirter makes use often existing code to work.

The many benefits it offers has led it to be used by independent app developers and even famous organizations

around the globe.

Also it is free to use an open source.

Some of the basic things about flirter which you should take note of.

Our number one fast development using flirter.

You can Haught reload in a manner of milliseconds to ensure your app can come to life in the shortest

time possible.

You can also make use of a vast range of fully customizable widgets which aid in building native interfaces

in the fastest manner possible.

I'm talking being able to build in minutes here.

Number two expressive and flexible UI are user interface.

Your app can't be successful if it isn't easy to use for people.

The best apps out there also featured the best and user experience.

So what flirter you get more tools to ensure the native and user experience is the best it can be.

The layered architecture gives you access to full customization enabling you to create user friendly

and interactive apps that have incredibly fast rendering rendering as well as expressive designs number

tree native performance.

Whether a person is using an Android and iOS device your app needs to offer them the experience they

expect the widgets in flirter are able to incorporate all of the critical platform differences to ensure

quality.

These black some differences include navigation scrolling icons and forks to the incorporation of DS

to differences your apps native performance on both Android and iOS devices is kept at optimum level.

Now that you have gained a basic understanding of Google flirter let me give you a quick indirection

introduction to dark.


3 . What is Dart?

What is dark when it comes to understanding darte you should know that it is an object already and did

and blossom defined language which you use C-style syntax which compiles optionally into javascript

d'arte offers a lot of support.

This means that it can support interfaces abstract classes make sense static typing and even a sound

type system.

Now all these terms might sound a bit too much for those of you who aren't familiar with such jargon.

Well let me make things easier for you.

Basically dark helps you with creating beautiful high quality experiences across all device screens

through a language that disclaimed optimize easy to use flexible tooling and very powerful and rich

frameworks coming to the next chapter.

I will be talking about and taking all of you over a brief history of mobile app development how it

evolved through the times and why you as a prospective ABB developer might end up making a name for

yourself in this field through Google furter or perhaps some other SDK you are comfortable with using.

So let's move on.


Seção 2: The History of Mobile App Development

4. Knowing You App History

As I've mentioned app development has grown tremendously over recent years.

As someone who is interested in entering this field it will do you good to get a quick overview of how

the mobile app development market has grown.

When they were first introduced cell phones were topped off as technology which was only used for making

phone calls.

However later on as we know the game changing invention of smartphones led to the opening of the mobile

app development door the software applications are as we call them apps work to get them to run or operate

on modern mobile devices such as tablets computers and smartphones.

As the years passed these apps were improved and now it seems to have become an important part of our

lives.

They seem to have seamlessly integrated into our lifestyle so starting with the beginning of the cell

phone.

Let's start this from all the way back.

Yes I'm talking about the beginning of the cell phone and yes the first ever cell phone call made.

For those of you who don't know the first cell phone call ever made was way back on April 3rd 1973 the

same call was made by Martin Cooper at Motorola.

Factually such a phone call was primarily a publicity stunt for the major company.

It wasn't until 10 years later since that ball that the first cell phone officially hit the market place

even then the journal Public wasn't able to use it.

Why.

Well because the dying not the A C A Poulson X the first cell phone in the market place cost a whooping

for \$2000 and it weighed approximately £2.

Yeah.

That's a lot.

Now of course this early Foon model did not have any applications.

I mean people likely didn't even know about apps back then it was in the 1990s when BBH was introduced

as the first operating systems that allowed apps during that specific time.

These devices were ones that included diaries spreadsheets word processors and databases.

Of course technology improved and TAAS BDA is work to become gettable of handling more apps.

It was open programming language which made it possible for users to build their own apps for the development

of custom apps.

Companies required Foster devices and yes even better operating systems.

You might not realize realize this now but the release of the BlackBerry smartphone which didn't get

there back in 2002 was heralded as a major achievement for technology companies.

This type of phone was able to seamlessly integrate wireless email and other features which were the

first for many during this time.

Java m e was very popular for phones and Beedi is why you might ask.

This was because it allowed users additional memory space.

Then in 2009 the release of Symbian opened the doors to even newer developments according to regard

to data at least 50 million devices adopted the Symbian operating system after it was released.

Even Nokia handsets Samsung devices and even LG phones started using the new operating system in order

to better themselves as brands.

So coming to the development of custom application which hit the mainstream Well once developers began

development began to speed up.

It didn't take long for apps to hit the mainstream and into Grant time.

We live in.

We basically have an app for every tank.

However going back to the history of it all back in 2007 the first iPhone was released by Apple the

App Store was added by the company very soon after that allowing users to find download and use apps.

In the beginning these apps were limited but it didn't take long for app developers to figure out the

untapped potential in this field.

Following suit the Android market gave people another platform for accessing apps and even to this day

there's a competition between Apple and Android app and I guess it's supposed to continue.

And while the competition between Android and Apple continues and developers look at the potential customer

base board flat platforms provide them.

Seção 3: Why Use Flutter?
5. Understanding why you should consider using Google
Flutter.


Doubted you'd know a bit more about slurper and how it can help you as an app developer.

Let's go over why you should consider using Slichter.

As mentioned before flirter is s the K This stands for a software development kit.

It is considered by many as an efficient way to create cross-platform mobile applications with an impressive

UI or user interface.

Take note that clutters way of designing views has similarities to web application.

That is where you can find a number of analogies to DML and CFS.

According to the developers of selector schlechter makes it easy and fast to build a beautiful mobile

app D-Wave flicker for most of cells.

Sounds great.

However for those of you who might not know about other cross platform solutions such as ionic re-act

native Zahm are in and more you might want to know a bit more about how Slichter can help.

There are certain benefits or flirter Stec might help you change your mind.

And you know urge you to start using it.

Some of you might have a lot of questions about flirter right now.

How does letter work.

Why is it considered to be innovative by others.

Why should they use it.

Etc..

And I hope to answer all of them in discourse.

And embark on benefit of flirter being immobile SDK for creating Krok cross-platform mobile applications

is that you can write one code and then run your app in both iOS and Android.

The code you write has to be written in dark.

So whichever language developed by Google Docs will look familiar to you.

If you have had experience of using Java before.

Take note that instead of using SML files you build a lay out dri.

Such a lay out is build from components of widgets that are nested your widget is a material app which

is the entire application and then you have discomfort which is Dumaine lay out structure then moving

inside.

You have the app bar which is like the android 2 toolbar and then a container as the body.

Now it is in this body that you put the lay out widgets such as buttons text etc. moving forward or

about why you should consider using clicker Here's a list.

Number one hot reload.

As mentioned before the Hawks reload can be considered as another best feature using hard to reload.

You can instantly build the projects you are working on as if you're building a web page simply change

something in the code.

Click Hawtry load and then you'll get to see the result instantly.

Number two an entire set of material design widgets that flirter you get to get the logged ecosphere

with built in UI components you should take note that there are two sets of rejects.

There's the material design which is for Android and Derrida's Cupertino which is for iOS.

You'll simply have to select the widget you want and then go from there.

Also there's no need for you to worry about the do widgets being too specific.

This means that even if you end up implementing some Cupertino are Maduna designed widgets it will end

up looking the same on every iOS and Android device out there.

So there's no need for you to worry about something in your app or even the app as a whole looking different.

When run on different devices However you can use different Android and iOS teams if you wish.

Also everything is a widget in flirter.

Yes even your app class the material app is a widget.

So is your entire lay out structure to scan for dimension.

So having everything as a widget allows you to use flirter to create impressive UI in a very simple

manner.

Number three.

Numerous packages even though it debuted dead.

Recently in 2007 Dean deflective community is very active and involved in making it better.

This has led to flatter being able to support many packages you have access to packages for opening

images sharing current and making HDTV requests accessing sensors storing your preferences.

Implementing firebase and the list goes on.

All of this support is for both iOS and Android.

Now that you have gone over the benefits of sluttier ask yourself Are you interested in using flirter.

No need to make a hasty decision.

I will be talking more about all of this as discourse continues.

Seção 4: How to Install Flutter?
6. Installing Flutter for Windows, Linux, and macOS

Number one your operating systems should be Windows 7 S-B 1 are later 64 bit you need at least 400 M-B

or three disk space.

Take note that does not include this place for Dools.

Talking about the tools you need.

Bovver shellfire point.

Or nor you need get.

This is G ID for Windows.

When they use good for Windows command prompt option.

If you have get for Windows is already installed.

Need to make sure you can run get command for the command prompt or partial installing flirter on Mac

OS to install and run flirter on Mac OS your development environment must meet these minimum requirements.

These are the operating system should be at least Mac OS 64 bit at least 700 M-B of free disk space.

Again this does not include disk space for Dools.

Now Dave note that flirter depends on a number of command line tools being available in your environment.

These are Bash and Diyar r m.

Good girl.

Unzip and even which number tree.

Moving on installing flirter on Linux to install and run flirter on Linux.

You need an operating system that is Linux 64 bit 600 M-B of free disk space.

This does not include disk space for Dools selector depends on some command line tools being available

in your environment.

These are again Bash and get Diyar.

R m.

Good girl.

Unzip and which the flexor test command depends on the library being available in your environment which

is as you can see lib G.O. you Daut s o dot one provided by me of baggage e.g. l AB lib Glou one me

are on Ubuntu are Debian.

You can see it on the slide so make sure to reserve the official selector website.

Do you have a more in-depth idea about the procedure which needs to be followed for you to install and

begin using flexor.



Seção 5: Benefits of Flutter
7. Benefits of Flutter

Building on a portion of the Course where I talked about why you should consider using flirter stock

a bit more about all of the benefits and it can offer you many developers recommend using flirter.

If you're just starting out in the app development field because of its friendly nature when it comes

to creating cross platform apps lets go over a list shall we.

Number one open source project flirter is an open source project allowing it to be available for use

as well yesterday by startups.

It offers you a lot of options to build the kind of app you wish to build for Android or iOS.

Furthermore being open source it gives rise to open collaboration allowing others to help improve or

do number two impressive Ed. integration by using flirter.

You can go ahead and keep on adding and subtracting edits during your app development process.

It offers impressive editor integration with Android studio and Visual Studio code.

This lead to smarter completions which are based on where the usual types function definitions and imported

modules number create dark fields like Java.

Why diet diet isn't a direct copy of Java.

The two are similar such similarities.

Help developers to make the shift to dark.

If they have been using Java for number four on the list we have 4 engineering managers engineering

managers can also use flirter if they have the need to lead more biol development teams using such an

SDK as an engineering manager.

You are able to create a single mobile app deaf team or development team helping you to unify the development

investments.

You can ship features faster lower your maintenance costs and transfer the same features sect to Android

and iOS simultaneously.

In short when you are using clutter you have access to a better widget features that are easy to use

and impressive editorial integrations for developing apps.

No wonder many developers have taken to using selector to not only create mobile apps but to also reach

a wider audience.

On Android as well as iOS.

Seção 6: How Much Experience as an App Developer
Should I have to use Flutter?

8. How Much Experience as an App Developer Should I
have to use Flutter?

This is the question many of you might currently have.

In short you don't need any prior immobile experience to learn and use flirter.

This SDK is very approachable to programmers who have an idea about imperative programming concepts

and object oriented concepts.

As long as you have a passion and interest in using clutter to create apps you'll find the process quite

easy and timesaving.

Let's talk about this a bit more.

Number one the reactive style when using flirter you'll need to begin somewhere to create an app for

iOS and Android.

This is why you need to be ready to work using a reactive framework.

Number do.

David you can't talk about selector without talking about the widget architecture it offers.

As mentioned everything is the widget and selector from your structure element to them and you are button

two very stylistic element you wish to use such as a color scheme and format everything.

It is a rigid insulator allowing you to create the kind of app you want without hassle.

You gain a lot of control over the app's execution composition object rendering and more number three.

Say bye bye to activity lifecycle management.

If you're someone who has dabbled a bit in app development you'll be familiar with activity lifecycle

management.

It just comes across as extra work doesn't it.

A peripheral activity if you may that doesn't directly add in the overall production process of your

app.

However what flirter you won't have to worry about activity lifecycle management.

This is because the clutter connecter patch helps to make all of the activities streambed did get dressed

and loaded in a synchronous manner.

Number for consistent 60 SPSS are frames per second.

Flirter is also useful for those looking to create a gaming or graphic heavy app selector is able to

give a consistent 60 frames per second rate due to being reactive in nature and using dark support.

You will get steady visuals in your developed app.

Number five the community support flirter also has a large community of expediencies as well as firing

developers that can help you out with any required support you need.

The community makes it easier for you to learn using flirter as well as make useful connections in the

app development field.

So moving on let's talk a bit about darte and why Slichter uses start.

Seção 7: Knowing About Dart
9. What is Dart and Why Use It?

During this course I have mentioned d'arte a lot as a small refresher.

Dart is a general purpose programming language which was originally developed by Google.

It was later approved as a standard by ECMA daks ECMA for 8 to be more precise.

You can use d'arte to build server web and mobile applications.

So why d'arte developers working at Google as well as others.

Don't you use darte for creating high quality apps for iOS.

And Android as well as the web.

So that's why it can be seen or it is seen as a great option when working with features aimed at client

side development.

Let's go to a list about Bart.

Number one productive dark syntax is clear and concise.

The overall tooling is very simple yet powerful.

You can identify subtle errors early through sound typing using darte.

You can also get numerous score libraries and thousands of packages.

Number two fast Dart can be termed as a language which offers you optimizing ahead of time on violation.

This help you do get predictably high performance and fast start up across mobile devices as well as

the web.

Number three workable for dark mobile apps do run natively on Android and iOS.

Dark compilers do A-R am an X 86 code.

Take note DEC for web app it dropped spiles to javascript and alost is approachable.

Many developers are familiar with d'arte do you do.

It's unsurprising object orientation and syntax.

You can easily get the hang of dark if you already know about Java are C++.

Now if you know a bit more about d'arte Lexi why you should consider learning it in 2018 as well as

why flirter makes use effect.

Seção 8: Why You Should Consider Learning Dart in
2018

10. Should You Consider Learning Dart in 2018 and
Beyond?

If you have been thinking about learning darte Here's a list that might help you make a decision.

Number one easy to learn.

As mentioned earlier Daryn guards share similarities with other common languages.

This also means that you might already know how to use d'arte without realizing it will be easy for

you to learn if you have experience with other object oriented languages such as Java are C++.

Even if you know some javascript learning Darb shouldn't be tough for you.

Another great thing is that dart supports both loose as well as strong typing.

This enables it to be easier when you're moving there from another language.

Number do a natively compiled shared code base.

Some of you might know that other frameworks allow you to share portions of the code base on different

platforms.

However dark is a bit different.

It allows you to write a single app which can then be used on both iOS and Android along with how being

compiled natively Dubost.

Now of course this is something others are allowed to do but darte is able to further allow the sharing.

You know you can I mean to say that allows you to share some of your code between are the entirety of

your corde the GUI not only mobile applications make Menke for different platforms meaning iOS and Android

but also for web as well as other guard applications too.

This allows you to share the majority of the non UI or let's say black specific code with Underdark

frameworks number to be productive by using dark you will get to experience for yourself how easy and

quick it is to create the layout as well as to add functionality for your app.

You can create Caly out into code creating a series of widget.

Remember what I told you that in flirter everything of the widget using such tools will surely help

you create what you want in the least time possible.

Number four compiles ahead of time and just in time when you are developing an app Avodart you can see

the changes you make instantly.

This means you won't have to go through the recompiling procedure and there's no need for you to wait

for the app to reload.

You just have to save the change and instantly see the changes.

This is possible because with such airmobile app development framework you can compile both ahead of

time.

R E or D as well as just in time.

R g d.

Now that you're aware of the reasons mentioned you are likely beginning to understand the benefit of

using darte.

Give it a try for yourself and see if it's something you wish to learn more about.

As an app developer moving further discourse of mine I let you know why flirter chose to use d'arte.


Seção 9: Why Does Flutter use Dart?

11. Why did Flutter Decide to Use Dart?
Flirter deciding to use d'arte wasn't a hasty decision.

Flirter use that tool.

A total of four primary dimensions for evaluation and considered all of the needs of the framework authors

and developers and end users.

It was founded while some languages met certain requirements.

It was dark there.

Scored highly on all of the evaluation dimensions that was checked by the flatter team and also met

all of the determined requirements and criteria.

You should know that Darkthrone dimes and compilers support the combination of two critical features

for flirter a parding to the flutter theme.

The first is the GAAP based fast development cycle which allows for shape changing and stateful Hawtry

load in the language with types.

As I mentioned before GAAP is just in time.

The second is the ahead of time our decompiler immense that emits efficient A-R import for fast startup

and predictable performance of a production deployments.

In addition the flirter team was able to work closely with the DAR community.

The community is active and continues to invest resources in improving darte when it comes to it being

used in flirter as an example.

When the team adopted darte decided to languish did not have an hour ahead of time or AOB toolchain

Freberg using native binary is such a feature is critical in achieving predictable high performance.

However now the language does have it because they are dark deam and they're building it for Lucker

the primary day a great day in with dark scored a scored high for the flutter deam were number one developer

productivity according to the theme.

One of letters main value propositions is that it saves engineering resources by letting developers

create apps for both iOS and Android with the same code base using a highly productive language accelerates

developers Forder and makes letter more attractive to them.

This was very important Dubow deflector framework team as well as the developers.

You should know that the majority of luck there is built in the same language ject as given to the users.

So the theme needs to stay productive at a hundred thousand lines of code without sacrificing approachability

or readability of the framework and widgets for developers.

Number two object orientation for flirter that theme vorn did a language that was suited to flusters

problem domain which is good again thing which you will use their experiences according to the team

the industry has multiple decades of expedience building user interface frameworks in object oriented

languages.

While they could have used a known object oriented language doing so would mean reinventing the wheel

to address a number of hard problems.

Furthermore a vast majority of developers already have experience with object oriented development making

it easier to learn how to develop their apps which selector now metry predictable high performance according

to the theme reflector.

They want to empower you the developers to create fast fluid user experiences.

So for them to meet this promise or aim they needed to be able to run a significant amount of developer

board during each animation frame.

This means that the team needed a language that could both deliver high performance as well as deliver

predictable performance without beating your bosses.

That could cause dropped frames number for fasc location in this point.

You should know that deflector framework makes use of a functional style flow which according to the

letter theme depends heavily on the underlying memory allocator efficient efficiently handling small

short lived location.

This file was developed in languages with this property and does not work efficiently in languages like

this facility.

So now you know why flutter decided to use d'arte and why you should be familiar with such a language.

And who knows you might want to use it as well.


Seção 10: Frequently Asked Questions About Flutter
12. What is inside the Flutter SDK?
Allow me to go over to frequently ask questions you might have in mind there disappoint.

The first question is what is inside the flirter SDK.

When it comes to answering what is inside deflector SDK.

Here's the list.

Number one heavily optimized Mumbai's first dual lead rendering engine with excellent support for text.

Then we have the Morgan re-act style framework rich set of widgets for Android and iOS which I have

said previously everything is a widget in flirter.

Number four it be nice for unit and integration tests.

Then we have enter interop and plug in API to connect to the system and take part D DST gais headless

best runner for running tests on Windows Linux and Mac command line tools for creating building testing

and compiling your apps.

13. Does Flutter come with a framework?

Does flutter come with the framework.

Yes.

As app developers you should know that flat-Earth ships with a modern framework which is inspired by

re-act flippers framework has been designed to be leared and customizable as a developer.

You can go ahead and select to use only part of the framework you have access you are a different framework

altogether.

The choice is yours.


14. Does Flutter come with widgets?
Does flutter come with Vineyard's As mentioned before which jerks out in the park and part of flutter.

So yes select their ships with a set of high quality McKeel design in Cupertino widgets layouts and

teams.

You can also go ahead and make your own widgets or even customize any of the existing widgets to create

the kind of app you want.

Again remember everything is a widget and flutter.


15. How does Flutter run my code on Android?

How does flirter run my on Android.

Some of you might be wondering how Slichter runs your code on and right to give you a simple answer.

According to the flooder team the Engine C and C++ code are compiled with androids and DK The Dark Lord

Boada SDK than yours are ahead of time.

AOP compiled into a native ARMM library.

That library is included in a runner and dreich project and the whole thing is built into any B.K. when

it is launched the app tends to load deflector library and any rendering in port or event handling and

so on are delegated to the compiled flirter and app code.

This process is also similar to the way many game engine and do work.


16. How does Flutter run my code on iOS?

Coming to how Echo does run by flirter on Io S according to the flattener team it is very similar to

how it's run on an android.

The Engine C C++ code compiled with LMM.

Again as mentioned the Dark Lord BODH the SDK and yours are ahead of time.

EO decompiled into a native ARMM library.

That library is included in a runner Iowas project and the whole thing is built into an dot IPA when

launched the app load deflector library and the same rendering import art event handling process draw

are delegated to the compiled flirter an app called.


Seção 11: Is Flutter the Future?
17. Is Flutter the Future?

After knowing so much about flirter it makes sense duping Gwydir are not just letters to the future.

When it comes to App Development Well I will try and answer this question in an unbiased way as possible

and then schlechter Debbie are dead.

Back in 2007 Dean the first stable release of flirter didn't take place until March 9 2018.

So you can see for yourself that it is still way too early to come up with a definition or a definitive

decision about whether or not collector is the future Arcand revolutionized the app development field.

A simple layering Behrami determines flirter success is by seeing if it has the ability to compare game

beat weird Riak native or not.

If you compare both of them right now you'll see that re-act native currently has the upper hand.

If the data about flirter does anything to go by some iPhone X users don't consider flirter to be the

best option for app development.

Furthermore re-act native showcase features numerous famous apps such as Instagram Facebook Skype A

B and B Wal-Mart and more.

Also some developers feel that Cupertino or Cupertino iOS library provided by flirter is too limiting

compared to the more than 35 elements in the material library.

There are around 14 components in the Cupertino library.

Maybe more will be added down the line.

Who knows.

Re-act native On the other hand has a lot to offer for iOS.

Now flicker might take the lead when it comes to user interface.

Our UI implementation.

But then again it is too soon to say anything about it right now.

Coming to guard which is the underlying programming language that is used by flirter there's not a lot

of adoption outside of Google.

That's why finding and hiring capable daar developers might be an issue for you.

Compared to developers specifically using d'arte javascript developers Borth them in a in the number

of professionals you'll be able to find just in 2018.

Having said all of this flirter does have some strong points which is attracting more users to work

number one dark happens to be faster than java script and in Slichter dark Gordis compiled directly

to the ARMM court number do you get great documentation to abart.

Also dark focuses more on fully custom you eyes are user interfaces which is something great which is

just something great for branded apps.

The last thing is flutter is called board development team continue working to make it better instead

of leaving everything to the community.

So if you are someone who is interested in checking out flirter you definitely should.

While it is too soon to judge whether or not slitter will become the next big thing in the app development

world.

It does offer you a lot of benefits which can help you create your app in a time saving manner.

Seção 12: Google Flutter ? Choose your path

18. Introduction - Google Flutter - Choose Your Path

In this portion of the course I will be going over whether or not you should opt for flirter in hopes

of making a career out of it and we'll be going over to freelancing options as well as the other possible

job vacancies offered by industries looking for individuals proficient in Google Slichter and darte.

So let's begin.


19. Can Flutter Lead to a Career For You?

As previously mentioned in the section about a flutter is the future Google Slichter is relatively new

and that is why even though it offers app developers a lot of benefits there is still some hesitation

about selecting it as a major SDK to make a career out of.

However there are all these exceptions to the norm and there are likely professionals out there that

are experiencing impressive career growth because of their expertise with regards to Google flicker.

The answer to this question depends on you.

Do you do being relatively new.

There aren't a lot of job vacancies specifically for people who know Google flirter.

That's why it is up to you to decide if you wish to opt for the freelancing route to test the waters

are if you want to apply for a position in some business.

More specifically if you want to go ahead and work for Google.

20. Freelancing as a Flutter Developer?

Starting with the freelancing options that you can avail as a selector developer and in a related sense

someone who knows darte the money you will be able to make depends on the type of project you will be

hired for.

Mostly people are looking for flutter developers because they want to hire someone to help them create

an app.

Such jobs usually include everything different and as well as a back and developing face.

You might even have to brainstorm with the person who hired you to polish the app up the payment for

a single project depending on what it entails.

Can range anywhere from \$200 to as high as Dan.

Thousand dollars.

And I'm talking American U.S. currency.

Not a lot of people have moved over to fliter.

However it is likely that in time more people will opt for flirter which will then give rise to higher

paying jobs for flirter developers.


21. Websites to Find Work as a Flutter Developer

Human go to the following list of that sites that offer work the kind of jobs you will be able to get

will depend on your experience and skill set.

The Web sites are up for Lance jobs.

Pro blogger I freelance 99 designs the creative grope guru project for hire.

Of course there are more Web sites that can offer you work as a flirter developer.

So all you need to do is to research about them online and see which Web site works best for you.


22. Working with a Business as a Flutter Developer

If you wish to be hired by a business as a floater developer then there are certain ones that might

hire you.

Google is your best option if you're experienced in schlechter.

You might end up being hired by Google as a technical program manager.

The responsibilities of such a job includes managing technical program programs and projects working

closely with engineers and technical staff to develop and track release milestones and schedules for

many moving parts that need to come together.

Developing a plan and schedule with well defined milestones managing communication of progress and status

updates within the core and extend those teams meaning the customer and partners and escalate issues

as necessary as assessing quality of resists true monitoring of incoming bugs and chord changes to identify

quality issues and trends developing tools and processes to improve software engineering productivity

according to current data.

The national average salary of a senior technical program manager in the United States is.

Wait for it one tree 8 0 6 9 dollars so that's like a hundred.

More than 100000 U.S. dollars yearly at sluttier developer.

You might also be hired by businesses as a software developer.

While the pay for the software developers can range from ninety thousand dollars do a bit more than

thousand dollars per year.

The software developer space is set to increase 22 percent from 2012 to 2022 so that might be a good

option for you as a profession.


23. Basic Skills to Have as a Flutter Developer

If you're thinking of starting your career as a flirter developer you should know about certain basic

skills.

These recommended skills are you should know how to render a screen using Mondial apps followed an apple

bar.

You should know how to lay out why a column and row you should know how to use container to grope and

content a guess.

You should know the use of text and image and how they can be used in conjunction.

You should know the workings of asset image and network image.

You should be creative and unique with your ideas.

You should be able to work on individual assignments as well as group projects.

You should be able to lead a team of developers if necessary.

You should be able to personalize the application a barbecue declines requirements.

You should have knowledge and know how about how dart works because I I have mentioned in the scores

you need to know about dark.

If you mean to use Google sluttier you should be able to use Jester's detector for making flexible and

customize buttons.

You should have good communication Anderton's skills.

As I said this is a list of recommended skills even if you don't know these skills right now you can

learn with expedients as you enter the field and continue on your journey as a Google selector developer.

24. Using Social Media to Find Jobs as a Flutter Developer


Using social media is another way for you to possibly get hired as a flirter developer to treat social

media platforms.

You can use are linked and this is a wonderful platform for finding jobs.

You only have to log in or sign up if you don't already have an account.

Then make your profile and start keeping track of company than people who you know well warmed or are

hiring flirter developers making sure your profile is up to date.

Is embarking when you are using linked and because potential employers can see it if they're like what

you have to offer.

They might come back to you about job Facebook.

Facebook is a popular social media platform.

It allows people to connect with one another from all over the world hence make use of this platform

and start to develop contacts.

You can join groups and pages that allow you to connect with people and companies that are looking to

hire people for work as well as depending on the scores.

As Google flirter developers Twitter to Twitter you can follow companies and people in the Google soccer

field to see if they are hiring.

You can also initiate a conversation with influential developers by replying to their tweets and building

that report with them to possibly help you in your career.


25. CV Creation Tips

Do be a successful flittered developer it is crucial that you take the first step right.

And that is your CV.

Keep your CV specific and to the point do not add in details that are of no use however also do not

forget to add information that is relevant.

Bear in mind that some companies have specific CV for Max that they ask you to follow when youre applying

for a job at their companies.

They may differ when compared to a standard CV in the sense that they may ask you only a few relevant

questions pertaining to the flirter developer job and nothing more.

Some CV tips include then promoting yourself as a floater developer.

It is important to highlight your experience even voluntary.

Try and keep away from buzzwords are terms that feel like an exaggeration.

Try to present your experience and what you can bring to the table without using words such as awesome

really spectacular highly creative etc..

Do you get a second pair of eyes to read your CV.

Sometimes a fresh pair of eyes will do it as a family member or a coworker that you dressed or even

a friend can help you spark certain mistakes.

Before you go ahead and submit your CV.


26. Other Tips to Help you as a Flutter Developer

There are many tips that didn't help you on your journey as a flirter developer.

Some of them are take as much time as required to do any real research potential job openings that are

available as a flirter developer.

You should work ethically and with full commitment to your job to build a good reputation for yourself

in this field.

As a freelancer you may hire a professional accountant services but keep track of your records and transactions

keep backup data for all of your transactions.

Do not go overboard when you start working with widgets.

Sometimes less is more.

Learn gradually set of goals and objectives for yourself that can motivate you.

Share your work with others that you trust in order to get constructive criticism.

Do not shy away from help and most importantly know your ward to.


27. Freelancing or a Regular Hire as a Flutter Developer?

So so should you opt for freelancing or a leg regular hire as a floater developer.

Well I don't have all the answers.

What I can do is try and guide you by presenting the facts so you can make your own mind.

As I've mentioned throughout discourse Google Strutter is relatively new and it will take time to determine

if it can hold the position against a famous SD case.

If you are someone who is interested in learning more about flirter and you happen to be passionate

about it you should.

Knowing how to use flirter is a good skill to have as an app developer.

Perhaps try and focus more on fire.

Java JavaScript C++ and half d'arte as an optional tool to use in the future.

If you're someone who knows a bit about unlettered and darte perhaps handle one or two freelancing gigs

and see how that turned out for you.

If you like experience then maybe you can apply for a position with a big company.

Also drying out a flutter darte internship at a local business can also help you make a final decision.

If you wish to continue it as a career again.

In the end it all depends on what you wish to achieve as an app developer.

Which languages and s DKs you find preferable to use and how much money you wish to make in your professional

career.


Seção 13: Summary and Conclusion
28. Summary and Conclusion

Thank you so much for keeping up with me to discourse I hope I was able to offer you the information

you required regarding Slackware and art and whether or not it's something you wish to learn more about.

As a quick summary Fluker has been created by Google to offer developers across Platform SDK that not

only saves time but also gives you a number of features which you can use to create apps that are reactive

and offered and and user expedience decs efficient.

It is recommended as a good option for developers who wish to create gaming apps are other apps that

are graphic rich again.

While it is too soon to judge whether flirter is the next big thing the fact which can't be denied is

that it has provided a number of developers an easier way to create the apps that they want.

So if you are interested in flirter and darte I recommend learning more about it.

Who knows you might end up liking it.

It has to offer you.

So again thank you so much for taking the time to go to discourse with me.

Stay blessed.

